Inefficient Concessions and Mediation

### 2021-01-17 notes.tex
add intuition for remaining mediator to-dos

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
						\begin{itemize}
							\item If you can sustain $e=1$ with no mediator, mediator can still be better
						\end{itemize}
					\item Sufficient condition for where welfare goes to positive $\infty$ to the left of the $e$ asymptote
						\begin{itemize}
							\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition. See end of Section~\ref{sec:WM1}
						\end{itemize}
					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable is strictly smaller than $\de^h$. \textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
							\begin{itemize}
								\item This is nice, but I'm not sure it helps with the narrative of the story.
									\begin{itemize}
										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
											\begin{itemize}
												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
												\item Should I compare grim trigger welfare to see which is higher?
											\end{itemize}
									\end{itemize}
							\end{itemize}
			\end{itemize}

>>>>

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
						\begin{itemize}
							\item Two differences: Mediator gets you some value of the gift $pTeg_M$; gift under mediator typically has to be larger--it takes more to disincentivize low type from lying because the payoff is better
						\end{itemize}
					\item If you can sustain $e=1$ with no mediator, mediator can still be better
						\begin{itemize}
							\item Again, if mediator is good, it's REALLY good.
							\item The benefit of $eg_M$ is muted versus $g^1$, but there is no harm from $g_M$ while there is harm from $g^1$. Cost of gift will always be larger under mediator because it goes to infinity at the optimal $e$
						\end{itemize}
					\item Sufficient condition for where welfare goes to positive $\infty$ to the left of the $e$ asymptote
						\begin{itemize}
							\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition. See end of Section~\ref{sec:WM1}
						\end{itemize}
					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable is strictly smaller than $\de^h$. \textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
							\begin{itemize}
								\item This is nice, but I'm not sure it helps with the narrative of the story.
									\begin{itemize}
										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
											\begin{itemize}
												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
												\item Should I compare grim trigger welfare to see which is higher?
											\end{itemize}
									\end{itemize}
							\end{itemize}
			\end{itemize}
